Fourmile

### 2022-08-02 fourmile_dataprocess.Rmd
loss/gains per yr

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
```

@@

@@

@@

@@

@@

USGS1 - USGS2

@@

ggplotly(diff3)

mean(diff_usgs1$q_m3s, na.rm=T)

>>>>

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
library(kableExtra)
```

@@

Average DS1 minus US1 difference

```{r DS1-US1_avg, echo=FALSE}

@@

diff_ds1_yr <- diff_ds1 %>%
  group_by(year(date)) %>%
  summarize(mean(q_m3s, na.rm=T))

kable(diff_ds1_yr, 
      col.names = c("Year", "Avg streamflow difference (m3/s)")) %>%
  kable_styling()

@@

Average USGS2 minus DS1 difference

```{r USGS2-DS1_avg, echo=FALSE}

@@

diff_usgs2_yr <- diff_usgs2 %>%
  group_by(year(date)) %>%
  summarize(mean(q_m3s, na.rm=T))

kable(diff_usgs2_yr, 
      col.names = c("Year", "Avg streamflow difference (m3/s)")) %>%
  kable_styling()

@@

USGS1 minus USGS2

@@

ggplotly(diff3)
```

Average USGS1 minus USGS2 difference

```{r USGS1-USGS2_avg, echo=FALSE}
mean(diff_usgs1$q_m3s, na.rm=T)

diff_usgs1_yr <- diff_usgs1 %>%
  group_by(year(date)) %>%
  summarize(mean(q_m3s, na.rm=T))

kable(diff_usgs1_yr, 
      col.names = c("Year", "Avg streamflow difference (m3/s)")) %>%
  kable_styling()
